---
title: "How far can you go for love on Airbnb? - The effect of Valentine's Day on
  Airbnb listings"
author: "Anouk Bor, Eva Bos, Bi Xuan Guo, Mandana Khabbazi, Indi Wieggers"
date: "2022-10-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)
```


# Introduction
For this study data from InsideAirbnb is used. To conduct our analysis of the effect of Valentine's day on Airbnb listings we extracted listing data from three European cities. Namely Rome, Paris and Madrid. After extracting the datasets per city they have been cleaned. Redundant columns are removed and new variables regarding the analysis are created. Finally the datasets of the seperate cities are merged into one complete dataset. 
The descriptions of all variables used are stated below, including the summary statistics.
Furthermore there are also plots included in the report that are generated regarding important variables from the analysis.
The main part of the report contains the analysis. --- more info ---
Finally the results of the study will be briefly discussed.

## Variable Descriptives
### Analysis 1
```{r}
#Analysis 1 
valentinesday_yes_no <- read.csv("../../gen/analysis/output/valentinesday_yes_no.csv")
valentinesday_yes_no
```
```{r echo=TRUE}
knitr::include_graphics('../../gen/analysis/output/price_valentinesday_boxplot.pdf')
```
### Boxplot price valentines day prices vs non valentines day price per city
```{r}
knitr::include_graphics('../../gen/analysis/output/boxplot_price_per_city.pdf')
```
### Histogram of prices --> meer uitleg/betere naam
```{r}
knitr::include_graphics('../../gen/analysis/output/histogram_prices.pdf')
```
### Analysis 2
The variable book consists of two categories; not booked (0) and booked (1), by looking at the mean (M=0.6978) in the data set we can conclude that airbnb's are more booked that not booked in the chosen time period  of this dataset. This conclusion can be verified by printing out the table and the histogram for the variable booked. On valentines day 53657 airbnb's were booked according to the data for the cities Rome, Madrid and Paris. If we compare this with a random date in February, we see that there is a small difference between both dates. Interesting is to see that on valentines day 53657 airbnb's are booked compared to the random generated date were 53826 airbnb's booked. We can conclude that on valentines day there are no more airbnb's booked in Rome, Madrid and Paris than on other random generated date. 

```{r}
knitr::include_graphics('../../gen/analysis/output/histogram_booked.pdf')
knitr::include_graphics('../../gen/analysis/output/histogram_total_bookings.pdf')
```

## Assumptions check 
### Analysis 1
```{r}

```

### Analysis 2
Before the logistic regression can be performed, we need to check for normality. A Shapiro-Wilk test is used to see if the data is normally distributed. The data set is too big for a the normality test and therefore a random sample is of 5000 is generated. The data is normally distributed because p = 0.0955 > 0.05, which means a logistic regression can be performed.  
```{r}

```


## Graphs
```{r}

```

## Analysis
```{r}

```

## Results