---
title: "How far can you go for love on Airbnb? - The effect of Valentine's Day on Airbnb listings"
author: "Anouk Bor, Eva Bos, Bi Xuan Guo, Mandana Khabbazi, Indi Wieggers"
date: "2022-10-07"
output:
    pdf_document: default
    html_document: default
---
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(stargazer)
```

# Introduction
This study uses data from InsideAirbnb. For our analysis of the effect of Valentine's Day on Airbnb listings, we collected listing data from three European cities that we assumed to be popular during Valentine's Day, namely Rome, Paris and Madrid. After extracting the datasets for each city, we cleaned these data. Redundant columns were removed and new variables related to the analysis were added. The datasets from the individual cities were then merged into one complete dataset.

A description of all variables used in the analysis, including relevant summary statistics, can be found in this report. Furthermore, the report includes several plots visualising the key variables from the analysis. The main section of the report contains the analysis that answers the research questions. The analysis consists of three parts, each with its own research question. The results of the three analyses are discussed. Ultimately, a conclusion on the effect of Valentine's Day on Airbnb listings will be drawn based on these analyses.

The following questions will be answered:

1. What is the effect of Valentine's Day on the price of Airbnb listings in the cities Rome, Madrid and         Paris?

2. Is there a significant difference in the number of bookings on Airbnb on Valentine's day? If so, is this     difference also greater in a city with a larger population?

3. Compared to other days in february, are relatively more Airbnb accommodations with one/two beds booked       during Valentine's Day?
    
# Variable Descriptives
## Prices
```{r echo=FALSE}
load('meanprice.RData')
load('meanvalentinesday.RData')
load('meanbooked.RData')
```

In order to analyze the influence of Valentine's Day on the prices of Airbnb accomodations, we used the metric variable 'price'. Furthermore, we created a dummy variable 'Valentinesday', which takes the value of 1 on Valentine's Day and 0 on any other day. The average price of an Airbnb listing from the full data is `r mean_price`. The mean of the 'valentinesday' dummy variable is `r mean_valentinesday`. 

```{r echo=FALSE}
valentinesday_yes_no <- read.csv("../../gen/analysis/output/valentinesday_yes_no.csv")
valentinesday_yes_no
```

We compare the price on Valentine's Day with the price on days two weeks before and after the celebration. The outcome of this comparison can be seen in the boxplot below. According to the generated boxplot, we can conclude that the difference between the averages price of accomodations on Valentine's Day and 'normal' days is very small. Furthermore, comparing the cities, we can conclude that the average price for Airbnb accomodations is highest in Paris. The average price is lowest in Madrid. This is verified by using the lapply function of the price per cities. 

```{r echo=FALSE}
knitr::include_graphics('../../gen/analysis/output/price_valentinesday_boxplot.pdf')
```

```{r echo=FALSE}
knitr::include_graphics('../../gen/analysis/output/boxplot_price_per_city.pdf')
```

## Bookings
To analyse the impact of Valentine's Day on bookings, we created a dummy variable for booked accomodations. The dummy variable booked consists of two categories; an accomodation that has not been booked (0) and an accomodation that has been booked (1). Looking at the mean `r mean_booked` in the dataset, we conclude that Airbnbs are more booked than not booked in the chosen period of this dataset (31 January - 28 February). This conclusion can be verified by printing out the table and the histogram for the variable 'booked'. 

A total of 53657 Airbnbs were booked in Rome, Madrid and Paris on Valentine's Day. If we take all other data from our dataset, an average of 53826 accommodations were booked for the cities. Therefore, we can conclude that there are not more accommodations booked via Airbnb during Valentine's Day, but even slightly less.

```{r echo=FALSE}
load('meanbooked.RData')
load('meanbeds.RData')
```

## Beds
The variable beds used in this analysis consist of two categories; zero or more than two beds (0) and one or two beds (1). Looking at the mean, `r mean_beds`, we can conclude that there are more than average Airbnbs with one or two beds in the dataset. The table below shows that on Valentine's Day, on average, more Airbnbs with one or two beds are booked than Airbnbs with more than two beds. This is the same for a day in February when it is not Valentine's Day. This can be checked from the boxplot below. We do need to take into account that there are many outliers.

```{r echo=FALSE}
knitr::include_graphics('../../gen/analysis/output/beds_booked_valentinesday.pdf')
load('shapiropvalue.RData')
```

--> HISTOGRAM

# Checking assumptions
Before the analyses are conducted to answer the research questions, some assumptions are first checked.

## Price analysis, Bookings analysis and Bed analysis
Before the logistic regression can be performed, it is necessary to check for normality. A Shapiro-Wilk test is used to see if the data are normally distributed. The whole dataset is too large for the normality test, so a random sample of 5000 observations is generated. The data are normally distributed because p = `r shapiro_test_pvalue` > 0.05, which means that a logistic regression can be performed.

The boxplot below shows that there are no extreme outliers for the price variable, so the data can be used to conduct a t-test. 

```{r echo=FALSE}
knitr::include_graphics('../../gen/analysis/output/price_valentinesday_boxplot.pdf')
```

However, if we look at the boxplot of the number of beds for the Airbnbs, we see many outliers and this should be taken into account when drawing conclusions based on this data.

```{r echo=FALSE}
knitr::include_graphics('../../gen/analysis/output/beds_booked_valentinesday.pdf')
```

```{r echo=FALSE}
load('ttestpvalue.RData')
load('pvaluemadrid.RData')
load('pvalueparis.RData')
load('pvaluerome.RData')
```
# Analysis
## Price analysis
This analysis will answer the following question: "What is the effect of Valentine's Day on the price of Airbnb listings in Rome, Madrid and Paris?". In order to answer this question, a t-test will be performed. 

First, we will look at the t-test per listing for all the cities studied. This t-test is not statistically significant, as `r ttest_pvalue` > p = 0.05. Additionally, the t-test results for the different cities Madrid, p = `r pvalue_madrid`, Paris, p = `r pvalue_paris`, and Rome, p = `r pvalue_rome`, are all > p = 0.05. This means that for all cities, the p-value of the t-test is not significant. Based on these values, we can conclude that none of the results of the t-tests are significant and that Valentine's Day has no significant effect on the price of the Airbnb listings in the cities. 

```{r echo=FALSE}
```

## Bookings analysis
This analysis will answer the following question: "Is there a significant difference in the number of bookings on Airbnb on Valentine's Day? If so, is this difference also greater in a city with a larger population?". In order to do this, a logistic regression will be performed. 

First we look at a logistic regression for all cities combined. After performing a logistic regression the summary of the regression will tell us that Valentine's Day has a significant effect on the number of bookings with a p-value that is smaller than 0.01. Looking at the exponents of the logistic regression, we can conclude that if Airbnbs change from not booked to booked, the value of Valentine's Day changes by 1.025085. The exponents by city of the logistic regression show that there are small differences by city. When Airbnbs are booked, Madrid decreases by a value of 0.9961, while Rome increases by a value of 1.005468 and Paris increases by a value of 1.006446. From the exponents, we can conclude that Madrid has the smallest change in value and Paris the largest when the Airbnbs in the dataset go from not booked to booked. To answer the question posed above, Valentine's Day has a significant effect on the number of Airbnb bookings when we look at the logistic regression and descriptive statistics. Based on the difference in population of the cities, there is a small change between the cities. Compared to the other cities, Madrid decreases rather than increases. Also, the largest change in value for Paris is not related to largest population of the cities. In fact, Paris has the smallest population of the three cities. Finally, a model fit is performed with a log likelihood ratio test to check whether the model is significant and H0 can be rejected. H0 tests whether all coefficients are zero. The log likelihood ratio test gives us a value of 0.009886, which is greater than 0.05. This is significant and so H0 can be rejected.

## Beds analysis
This analysis will answer the following question: "Compared to 'normal days', are relatively more Airbnb accommodations with one/two beds booked during Valentine's Day?". A logistic regression will be performed. 

First, we will look at a logistic regression for all cities combined. After performing a logistic regression we can conclude that Valentine's Day has no significant effect on beds, because the regression has no significant p-value. Looking at the exponents of the logistic regression, we can conclude that if Airbnbs change from zero or more than two beds to one or two beds, the value of Valentine's Day changes by 0.998608. If we look at the exponents by city of the logistic regression, we see that there are small differences by city. If Airbnbs are booked, Madrid will increase by a value of 1.000008. However, Rome will decrease by a value of 0.9998941 and Paris by a value of 0.9979593. From the exponents, we can conclude that Madrid has the smallest and the only one with a positive change in value, while Rome has the largest negative change in Airbnbs in the data set, going from zero or more than two beds to 1 or two beds. To answer the question posed above, there is no significant difference of Valentine's Day on the number of beds, so between zero or more than two beds and 1 or 2 beds. Looking at the difference in population of the cities, there is no significant difference between the cities. However, there is a difference in direction as only Madrid is positive. Finally, a model fit is performed with a log likelihood ratio test to check whether the model is significant and the H0 can be rejected. H0 tests whether all coefficients are zero. The log likelihood ratio test gives us a value of 0.7905802. 0.7905802 is greater than 0.05 and therefore significant, allowing the H0 to be rejected.

## Results
From the first analysis, we can conclude that there is no statistically significant finding on the influence of Valentine's Day on the price of Airbnb listings. Therefore, we cannot draw any conclusions about the influence of Valentine's Day on the price of listings in Madrid, Paris and Rome. From the second analysis we can conclude that Valentine's Day has a significant effect on the number of bookings. However if we look into the cities separately we see no significant effect and therefore only can conclude that for Rome, Madrid and Paris together, Valtenine's Day has an effect. Finally, we also found no statistically significant results in the last analysis on the number of beds. Again, we cannot conclude that Valentine's Day has an impact on the number of beds per Airbnb booking. This again means that there is not significant influence of Valentine's Day on the number of beds per Airbnb booked in Madrid, Paris and Rome.
